Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations in the Upper Salmon River, Idaho

### 2021-12-21 analysis/paper/paper.Rmd
compiling bioenergetics results

```{r shoup-temp-data}
shoup_temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

```{r read-bio-outputs}
# full year, no growth
full_yr_no_growth = read_csv(here("analysis/data/raw_data/2020 Bioenergetics 1 year.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# full year, 10% growth
full_yr_10p_growth = read_csv(here("analysis/data/raw_data/2020 Bioenergetics 1 year 10% growth.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# an alternative model
alternative_mod = read_csv(here("analysis/data/raw_data/Bioenergetics 32 fish 68 inverts.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

# Fall emigration period (9/1 - 11/17), no growth
fall_only_no_growth = read_csv(here("analysis/data/raw_data/78_day_bioenergetics.csv")) %>%
  clean_names() %>%
  mutate(date = as.Date(date, format = "%m/%d/%y")) %>%
  mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>%
  mutate(month = month(date))

>>>>

```{r shoup-temp-data, eval = F}
shoup_temp_df = read_tsv(here("analysis/data/raw_data/USGS_13307000_Salmon_River_Nr_Shoup.txt"),
                   comment = "#") %>%
  rename(discharge_cfs = `47768_00060`,
         discharge_cfs_cd = `47768_00060_cd`,
         gage_ht_ft = `47769_00065`,
         gage_ht_ft_cd = `47769_00065_cd`,
         water_temp_c = `47773_00010`,
         water_temp_c_cd = `47773_00010_cd`)

@@

```{r read-bio-outputs}
fmt_bio_out = function(x) {
  x = x %>%
    clean_names() %>%
    mutate(date = as.Date(date, "%m/%d")) %>%
    mutate(cum_cons_fish_g = cumsum(cons_fish_g)) %>% 
    mutate(month = month(date))
  return(x)
}

# fall, fish 10% - 90%
fall_f10 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I90_F10.csv")) %>% fmt_bio_out()
fall_f20 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I80_F20.csv")) %>% fmt_bio_out()
fall_f30 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I70_F30.csv")) %>% fmt_bio_out()
fall_f40 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I60_F40.csv")) %>% fmt_bio_out()
fall_f50 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I50_F50.csv")) %>% fmt_bio_out()
fall_f60 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I40_F60.csv")) %>% fmt_bio_out()
fall_f70 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I30_F70.csv")) %>% fmt_bio_out()
fall_f80 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I20_F80.csv")) %>% fmt_bio_out()
fall_f90 = read_csv(here("analysis/data/raw_data/Bioenergetics_Fall_I10_F90.csv")) %>% fmt_bio_out()

# spring, fish 10% - 90%
spring_f10 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I90_F10.csv")) %>% fmt_bio_out()
spring_f20 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I80_F20.csv")) %>% fmt_bio_out()
spring_f30 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I70_F30.csv")) %>% fmt_bio_out()
spring_f40 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I60_F40.csv")) %>% fmt_bio_out()
spring_f50 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I50_F50.csv")) %>% fmt_bio_out()
spring_f60 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I40_F60.csv")) %>% fmt_bio_out()
spring_f70 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I30_F70.csv")) %>% fmt_bio_out()
spring_f80 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I20_F80.csv")) %>% fmt_bio_out()
spring_f90 = read_csv(here("analysis/data/raw_data/Bioenergetics_Spring_I10_F90.csv")) %>% fmt_bio_out()

# average size of DSR and NRR juveniles
avg_DSR_g = 10.3
avg_NRR_g = 10.9

# compile fall results
fall_results = fall_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = fall_f20$cum_cons_fish_g,
         f30_g = fall_f30$cum_cons_fish_g,
         f40_g = fall_f40$cum_cons_fish_g,
         f50_g = fall_f50$cum_cons_fish_g,
         f60_g = fall_f60$cum_cons_fish_g,
         f70_g = fall_f70$cum_cons_fish_g,
         f80_g = fall_f80$cum_cons_fish_g,
         f90_g = fall_f90$cum_cons_fish_g) %>%
  mutate( across(contains('_g'),
                 .fns = list(n = ~./avg_DSR_g),
                 .names = "{col}_{fn}") )

rm(fall_f10, fall_f20, fall_f30, fall_f40, fall_f50, fall_f60, fall_f70, fall_f80, fall_f90)

# compile spring results
spring_results = spring_f10 %>%
  select(date, temperature_c, cum_cons_fish_g) %>%
  rename(f10_g = cum_cons_fish_g) %>%
  mutate(f20_g = spring_f20$cum_cons_fish_g,
         f30_g = spring_f30$cum_cons_fish_g,
         f40_g = spring_f40$cum_cons_fish_g,
         f50_g = spring_f50$cum_cons_fish_g,
         f60_g = spring_f60$cum_cons_fish_g,
         f70_g = spring_f70$cum_cons_fish_g,
         f80_g = spring_f80$cum_cons_fish_g,
         f90_g = spring_f90$cum_cons_fish_g) %>%
  mutate( across(contains('_g'),
                 .fns = list(n = ~./avg_NRR_g),
                 .names = "{col}_{fn}") )

rm(spring_f10, spring_f20, spring_f30, spring_f40, spring_f50, spring_f60, spring_f70, spring_f80, spring_f90)
